Rusty Linux: Advances in Rust for Linux Kernel Development

### 2024-06-06 paper.tex
Update on Overleaf.

Comparing performance, throughput and latency between different systems is very difficult. For
example, several of the operating systems written in Rust, such as Tock, are a complete rethinking of
how an operating system is designed, and Rust for Linux (RFL) is still relatively new and has not had
the benefit of decades of incremental performance improvements like components that are written in
C. Additionally, direct comparisons between a Monolithic kernel, Micro-kernel, and Unikernel, or
comparisons between a Real Time Operation System (RTOS) and a General Purpose Operating System, are
not directly meaningful due to the vastly different goals of each system. Therefore, we will focus
more on the overall efforts that are specific to the Rust programming language and the challenges
presented. We summarize our findings in table~\ref{tab:RQ2}.

>>>>

Comparing performance, throughput and latency between different systems with different architectures is very difficult. For
example, several of the operating systems written in Rust are a complete rethinking of
how an operating system is designed~\cite{Boos2020-zh} while others run entirely in kernel space~\cite{Lankes2019-cm}. Additionally, direct comparisons between a Monolithic kernel, Micro-kernel, and Unikernel, or
comparisons between a Real Time Operation System (RTOS) and a General Purpose Operating System, are
not directly meaningful due to the vastly different goals of each system and the overhead that is imposed by the hardware~\cite{{Arnott2012-fl}. Therefore, we will focus
more on the overall efforts that are specific to the Rust programming language and the challenges
presented. We summarize our findings in table~\ref{tab:RQ2}.
